MetaTracts - A Method for Robust Extraction and Visualization of Carbon Fiber Bundles in Fiber Reinforced Composites

### 2014-08-26 chapters/MetaTracts.tex
updated copy added a section

\begin{figure}[h]
\centering
	\subfloat[]{\includegraphics[width=0.49\linewidth]{imagesMT2014/MT_crop16_MT.png}}
	\subfloat[]{\includegraphics[width=0.49\linewidth]{imagesMT2014/length_distribution.PNG}}
	\caption{(a) MetaTracts colored according to mean orientations. (b) length distribution of individual MetaTracts for a particular bundle.}
	\label{fig:length_distribution}
\end{figure}

@@

\section {Voxelization and surface extraction}
\label{sec:vis}
Apart from direct visualization of the MetaTracts, we show two simple extensions of MetaTracts. The first way is to voxelize the original volume according to the clusters each voxel is associated with.
The second is to extract the corresponding surfaces from the voxel data by binarizing the volume per cluster and extracting the isosurface from the binary volume by marching cubes algorithm. To voxelize the space,  we compute a neighborhood around each voxel. We then enumerate the number of voxels of each class (cluster) in this neighborhood. The voxel is then assigned to the class with the maximum number of elements in the neighborhood.  Intuitively this is a modification of the flood-fill algorithm. Figure~\ref{fig:mesh} and Fig.~\ref{fig:prepreg}D shows examples od extracted meshes.

\begin{figure}[h]
  \centering
   \includegraphics[width=0.9\linewidth]{imagesMT2014/mesh2.png}
   \caption{Two of the extracted triangle meshes.}
   \label{fig:mesh}
   \end{figure}

@@

\begin{figure}[h]
\centering
	\includegraphics[width=0.5\textwidth]{imagesMT2014/all_clusters.PNG}
	\caption{(A) Orientation wise decomposition of data set Figure~\ref{fig:data-char}A into the extracted bundles and (B) all of them combined.}
	\label{fig:crop-16-decomp}
\end{figure}
\begin{figure}
\centering
	\includegraphics[width=0.5\textwidth]{imagesMT2014/crop-6-J.PNG}
	\caption{Data set with flat thin and compact bundles. A shows the volume rendering and a 2D slice, B shows the clusters according to individual orientation.C shows the complete result. D shows the cropped part of the mesh generated from the marked bundle.}
	\label{fig:prepreg}
\end{figure}
\begin{figure}
\centering
	\includegraphics[width=0.5\textwidth]{imagesMT2014/Graph_crop16.PNG}
	\caption{Number of tracts and median, minimum and maximum length of individual MetaTracts in the orientation cluster Fig.~\ref{fig:orientation_clustering}C, clustered into 10 clusters (Fig.~\ref{fig:crop-16-decomp}A top). The unit for length is the grid cube length. Figure~\ref{fig:length_distribution}(b) shows the length of individual MetaTracts in cluster 6.}
	\label{fig:len_dist_crop16}
\end{figure}

@@

%\begin{figure}
%\centering
%\subfloat[]{\includegraphics[width=0.25\linewidth]{imagesMetaTracts/glass-scalar.eps}}
%  \subfloat[]{\includegraphics[width=0.25\linewidth]{imagesMetaTracts/glass-scalar-slice.eps}}
%  \subfloat[]{\includegraphics[width=0.25\linewidth]{imagesMetaTracts/glass-cluster-b.eps}}
%  \subfloat[]{\includegraphics[width=0.25\linewidth]{imagesMetaTracts/glass-cluster-a.eps}}
%  \caption{Our algorithm on a data set made of glass fibers. (a) The scalar dataset, (b) Depicts a slice from the data set, the  fibers are clearly demarcated from the rest of the matrix as oppose to the type of data  where it is hard to distinguish the fibers (Fig. \ref{fig:orig_data}). (c) The result of the MetaTracts process, the colors are to help visualization. (d) The result of the orientation based clustering, the two clusters are marked red and yellow.}\label{fig:glass}
%\end{figure}

@@

%\textit{Glass Fibers}, While the core advantages of our approach are in cases when the individual fibers are not discernible, our approach also works on data where the fibers are relatively well separated. Fig. \ref{fig:glass} shows our framework applied on a glass  data set (350x350x300 in size) with an isotropic resolution of $2 \mu m$. Fig. \ref{fig:glass}b shows a slice from the original dataset, (comparison with Fig. \ref{fig:orig_data} shows the individual fiber separation is easier in this case.) 
% Fig.~\ref{fig:glass}c shows the result of the MetaTracts extraction process. Fig~\ref{fig:glass}d shows the results of the orientation based clustering into two clusters (reds and yellows). TODO: with this as the ground truth, add noise and repeat experiment, to show robustness.

@@

%\begin{figure}
%  \centering
%\includegraphics[width=0.2\linewidth]{imagesMetaTracts/compare-clus-1.eps}
%\includegraphics[width=0.2\linewidth]{imagesMetaTracts/compare-clus-2.eps}
%  \caption{Comparison of clustering approaches.(a) Orientation clustering into 2 classes followed by hierarchical clustering into 3 classes each. (b)Hierarchical clustering into 6 classes.}
%  
% \label{fig:fiber-clus-2}
%\end{figure}

%\subsection {Proximity measures}
%\textbf{weighted undirected graph}
%In DT-MRI, each voxel is assigned a tensor that describes local water diffusion. In our case the Hessian is error prone

@@

\section{Parameter choices}
\label{sec:param_choices}
The critical parameters are $K$ for the K-means in orientation based clustering and $h$ for the hierarchical clustering. K denotes the number of major directions. Which is generally known a priori or can be easily estimated by looking at the weaving pattern. 
Our framework is robust to the choice of $h$ (Section~\ref{sec:results}). Large $h$ keeps the major bundles intact. For example, in  Fig.~\ref{fig:len_dist_crop16}, where $h$ was set to ten while the ground truth was five, we observe that the major clusters remain well segmented and thus small clusters can be removed if they have too few elements. This is an appealing trait of the proximity based clustering, thus providing good results even when exact $h$ might be unknown.

>>>>

\begin{figure}[h]
\centering
%	\subfloat[]{\includegraphics[width=0.49\linewidth]{imagesMT2014/MT_crop16_MT_2.png}}
	\subfloat[]{\includegraphics[width=0.49\linewidth]{imagesMT2014/MT_crop16_MT_2.PNG}} 
	\subfloat[]{\includegraphics[width=0.49\linewidth]{imagesMT2014/length_distribution.PNG}}\\
%	\subfloat[]{\includegraphics[width=0.9\linewidth]{imagesMT2014/mt_crop_16_orient.PNG}}
	\caption{(a) MetaTracts colored according to mean orientations. (b) length distribution of individual MetaTracts for a particular bundle.}
	\label{fig:length_distribution}
\end{figure}

@@

\section {Voxelization and surface extraction}
\label{sec:vis}
Apart from direct visualization of the MetaTracts, we show two simple extensions. The first way is to voxelize the original volume according to the clusters each voxel is associated with.
The second is to extract the corresponding surfaces from the voxel data by binarizing the volume per cluster and extracting the isosurface of the largest connected component from the binary volume. To voxelize the space,  we compute a neighborhood around each voxel. We then enumerate the number of voxels of each class (cluster) in this neighborhood. The voxel is then assigned to the class with the maximum number of elements in the neighborhood and Fig.~\ref{fig:prepreg}D shows the result of voxelization{\tiny }. Figure~\ref{fig:mesh} shows examples of extracted meshes.

@@

\begin{figure}[h]
\centering
	\includegraphics[width=0.5\textwidth]{imagesMT2014/all_clusters.PNG}
	\caption{(A) Orientation wise decomposition of data set Figure~\ref{fig:data-char}A into the extracted bundles and (B) all of them combined.}
	\label{fig:crop-16-decomp}
\end{figure}
\begin{figure}[h]
  \centering
   \includegraphics[width=0.9\linewidth]{imagesMT2014/mesh.png}
   \caption{Extracted meshes. (A) shows two of the extracted meshes separately. (B) Shows two different views of the combined meshes.}
   \label{fig:mesh}
   \end{figure}
\begin{figure}
\centering
	\includegraphics[width=0.5\textwidth]{imagesMT2014/crop-6-J_2.PNG}
	\caption{Data set with flat thin and compact bundles. A shows the volume rendering and a 2D slice with one of the boundaries marked in red, B shows the clusters according to individual orientation.C shows the complete result. D shows the voxelization of C.}
	\label{fig:prepreg}
\end{figure}
\begin{figure}
\centering
	\includegraphics[width=0.5\textwidth]{imagesMT2014/Graph_crop16.PNG}
	%\includegraphics[width=0.23\textwidth]{imagesMT2014/Graph_crop16_3.PNG}
	\caption{Number of tracts and median, minimum and maximum length of individual MetaTracts in the orientation cluster Fig.~\ref{fig:orientation_clustering}C, clustered into 10 clusters (Fig.~\ref{fig:crop-16-decomp}A top). The unit for length is the grid cube length. Figure~\ref{fig:length_distribution}(b) shows the length of individual MetaTracts in cluster 6.}
	\label{fig:len_dist_crop16}
\end{figure}

@@

@@

@@

@@

\section{Parameter choices}
\label{sec:param_choices}
The critical parameters are $K$ for the K-means in orientation based clustering and $h$ for the hierarchical clustering. K denotes the number of major directions. Which is generally known a priori or can be easily estimated by looking at the weaving pattern. 
Our framework is robust to the choice of $h$ (Section~\ref{sec:results}). Large $h$ keeps the major bundles intact. For example, in  Fig.~\ref{fig:len_dist_crop16}, where $h$ was set to ten while the ground truth was five, we observe that the major clusters remain well segmented and small clusters can be removed if they have too few elements (clusters 2,3,4 and 5 in Fig.~\ref{fig:len_dist_crop16} all have less than 10 elements). This is an appealing trait of the proximity based clustering, thus providing good results even when exact $h$ might be unknown.
